---
title: "Module evauation"
date: June 2017
output: tufte::tufte_html
---

```{r}
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, message=F, warning=F)
library(tidyverse)
library(pander)

options(scipen=1, digits=3)
panderOptions('round', 3)
panderOptions('keep.trailing.zeros', TRUE)
```



# Setup and data processing

An example of the survey is here: http://www.psy.plymouth.ac.uk/Admin4/ModEvaluation/(S(3dc4nde5u5gop1ffehmd014a))/psyc201.aspx

Data are downloaded from the tech office site as 3x csv files for modules, staff and overall. Set the filenames in the first code block below:



```{r}
modules_file <- "tblmodule_20_Jun_2018.csv"
staff_file <- "tblStaff_20_Jun_2018.csv"
overall_file <- "tblOverallMSc_20_Jun_2018.csv"
```


```{r}
modules <- read_csv(modules_file)
staff <- read_csv(staff_file) 

studentprogrammes <- bind_rows(
  staff %>% select(userkey, program),
  modules %>% select(userkey, program)
) %>% distinct

score_labels <- data_frame(
  value = 1:5,
  label = c("Very Positive", "Positive", "Negative", "Very negative", "Not Applicable")
)

prognames <- data_frame(
  program = c(501,502,503,551),
  progname = c(
    "MSc Psychology", "PRM", "MSc Exchange - Psychology", "MPsych"
  )
)


question_labels <- data_frame(
  variable = c(paste("q", 1:11, "a", sep=""), paste("q", 1:11, sep="")),
  question_label = rep(c(
    "The Stage Handbooks",
    "Programme or Pathway lead",
    "Office hours",
    "Email.",
    "Psychology technicians",
    "Careers",
    "Faculty Student Reception in the Rolle building",
    "Range of topics covered in this term.",
    "Range of assessments.",
    "Teaching methods.",
    "Overall experience of Psychology this term"
  ), 2)
)

overall <- read_csv(overall_file) %>% 
  left_join(., studentprogrammes, by=c("userkey", "program")) %>% 
  mutate(program = ifelse(str_detect(program, "Research Methods"), 502, program)) %>% 
  mutate(program = ifelse(str_detect(program, "MSc Psychology"), 501, program)) %>% 
  mutate(program = ifelse(str_detect(program, "MPsych"), 551, program)) %>% 
  mutate(program = as.numeric(program)) %>% 
  left_join(., prognames, by="program") %>% 
  glimpse


```



# Programme level reports


## Numeric data
```{r, fig.width=10, fig.height=10}

qdata <- overall %>% 
  select(starts_with("q"), Year, progname) %>% 
  select(-ends_with("a"), Year, progname) %>% 
  reshape2::melt(id.var=c("Year", "progname")) %>% 
  mutate(value=as.numeric(value)) %>% filter(!is.na(value))

mypal <- rev(c('#bababa', '#d7191c','#fdae61','#a6d96a','#1a9641'))
qdatasumm <- qdata %>% 
  left_join(., question_labels) %>% 
  left_join(., score_labels) %>% 
  mutate(value=factor(value, labels=score_labels$label)) %>% 
  group_by(Year, progname, question_label, value) %>% 
  summarise(n = n())

p <- qdatasumm %>% 
  filter(progname %in% c("MPsych", "PRM")) %>% 
  filter(value!="Not Applicable") %>% 
  ggplot(aes(x=question_label, y=n, fill=value)) + 
  geom_bar(stat="identity", position="fill") + 
  facet_grid(Year~progname) + 
  xlab("Question") + ylab("Proportion") +
  scale_fill_manual("", values=mypal) + coord_flip()

ggsave('quant.by.prog.pdf', p)
p
```

## Overall comments

```{r}
programmefeedback <- overall %>%
  select(progname, Year, matches("q\\w+a")) %>% 
  reshape2::melt(id.vars=c("Year", "progname")) %>% 
  left_join(., question_labels) %>% 
  filter(!is.na(value) & length(stringr::str_trim(value))>10) %>% 
  mutate(question = naturalsort::naturalfactor(variable)) %>% 
  arrange(question) %>% 
  select(progname, Year, question_label, value) 

programmefeedback %>% 
  arrange(-Year, progname, question_label) %>% 
  filter(progname=="PRM") %>% 
  pander::pander(., justify=rep("left", 4))
```






# Staff ratings and feedback

### Numeric (not this plot is NOT anonymised)

```{r, fig.fullwidth=T}
p <- staff %>% 
  filter(!str_detect(module, "PSYC")) %>% 
  select(staff, explaining, interesting, overall, year) %>% 
  group_by(staff, year) %>% 
  mutate(nresp = n()) %>% 
  filter(nresp > 2) %>% 
  mutate(staffn = paste(staff, " (N = ", nresp, ")", sep="")) %>% 
  select(-nresp) %>% 
  reshape2::melt(id.vars=c("staff", "staffn", "year")) %>% 
  filter(year > 2016) %>% 
  filter(value > 0) %>% 
  ggplot(aes(variable, value)) + 
  geom_boxplot() + 
  facet_wrap(~staff) +
  geom_hline(yintercept = 2, color="red") + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

ggsave('staff.pdf', p, width=6, height=10)
p
```




## Staff and module reports for PRM/MPsych

This saves reports per-staff-member into a local directory (as html) for distribution.

```{r}
staff %>% 
  filter(!explaining==0) %>% 
  filter(str_detect(module, "PSY5|PSYC7")) %>% 
  select(staff, year, module, comments, explaining, interesting, overall) %>% 
  arrange(staff) %>% 
  group_by(staff, year) %>% 
  do(., {
    f <- paste0("reports/", .$year[1], "-", .$staff[1], ".html")
    print(xtable::xtable(.), type="html", file=f);
    data_frame(staff=.$staff[1])})

modules %>% 
  filter(!str_detect(module, "PSYC")) %>% 
  select(module, year, semester, comments, workload, feedback, learning) %>%
  group_by(module, semester, year) %>% 
    do(., {
    f <- paste0("reports/", .$year[1], "-", .$module[1], "_semester", .$semester[1], ".html")
    print(xtable::xtable(.), type="html", file=f);
    data_frame(module=.$module[1])})

```

